Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny July20 10

The governing equation for $u(\xx,t)$ is obtained by computing the domain variation of the free energy $F$ \cite{Fu20}:
We obtain
a screened Laplace equation boundary value problem as a model for the hydrophobic interaction between water and JPs:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ gives the degree of hydrophobicity the
particle-solvent interface.

@@

The boundary condition on JP can be classified into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
these three categories correspond to three characteristic values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles and 60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayers for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.

Figure~\ref{fig:relax}(a)shows the initial configurations with orientations of 198-particle and 60- particle cases,
respectively. 
Case (i) with $b = 1$, mimicks an amphiphilic particle.
The boundary condition $g$ is everywhere nonnegative,
takes the value $0$ on the
hydrophilic head (green),
and takes the maximum value $a$ on the
hydrophobic tail (red). 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for 60-particle run.
Both cases form bilayers with multiple components.

In case (ii) with $b = 1$, the boundary condition is everywhere positive.
It takes the maximum value $3a$ on tail (red) and the
minimum value $a$ on the head side (yellow). 
Both sides of the Janus particle are hydrophobic but
more so on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers form multilamella structures.
The number of folds depends primarily on the number of particles.
Figure~\ref{fig:relax}(c), for example, shows a
multilamellar structure with four layers and one with two layers in the inset.

In case (iii) with $b=1$,
a water structure with
positive/negative charge is possible \cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
square grid and the orientations alternate
between layers (Figure~\ref{fig:relax}(d)).

@@

\subsection{Bilayer configurations in a shear flow}
To begin, we place the bilayer structure (Figure~\ref{fig:relax}(b), inset)
in the shear background flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y\cdot\xx){\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate and ${\bf e}_x$ and ${\bf e}_y$
are horizontal and vertical unit vectors, respectively.  
Figure~\ref{fig:BC1_shear}(a)--(c)
shows snapshots of the vesicle when $\dot\gamma= 0.05,0.075,0.01$
at $t = 0.5$ $\upmu$s.
The general pattern consists of a rotating body.  The various bilayer components
detach and reattach throughout so that the boyd is continuously changing morphology.
The supplementary movies show that these bilayers merge and form a worm-like shape in higher 
shear flows.

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
 The streamlines are plotted in the background. 
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
  }
\end{figure}

In terms of deformations, 
the free energies 
are relatively constant (Figure~\ref{fig:BC1_shear}(d)),
with the overall changes in the range of a few kT/nm.  Note that the free energy takes
the form of a line tension because the simulations are two-dimensional.

An interesting feature of the simulations is that the $\tilde S_2$ order parameter
is on the average increasing (Figure~\ref{fig:BC1_shear}(e)).  In the initial configuration,
the structure has three or four components.  Under the shear flow, the detachment and reattachment
results in an overall decrease in the number of components.  This suggests that
the shear flow perturbs the local equilibrium obtained from a random initial condition
to an alternate local equilibrium with greater orientational order.

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
  \end{center}
\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
}
\end{figure}

Finally, the strain parameter diverges in the large shear flow rate cases (Figure~\ref{fig:BC1_shear}(f))
because the components eventually completely separate and move away from one another
under the shear flow.

We reinitialized the case (i) configuration with particles arranged in the pattern of a single, circular vesicle.
This shape is also a local equilibrium, with somewhat less energy than the disordered state c.f.,
Figure~\ref{fig:BC1_shear}(d) and Figure~\ref{fig:Ves_shear} (d).
Our previous paper \cite{Fu2022_JFM} studied
The vesicle in a shear flow undergoes the familiar tank-treading deformation (Figure~\ref{fig:Ves_shear} (a)--(c)),
and based on previous results (\cite{Fu2022_JFM}),
we investigate the cases $\dot\gamma=0.05, 0.066, 0.075$.

Unlike the multiples component case, 
the energies for the vesicle case show jumps from the baseline value $30$ kT/nm to 32 kT/nm
signaling the rupture of the vesicle into multiple components
(Figure \ref{fig:Ves_shear}(d), long and short dashed curves).
After this initial break, the energies are more or less constant.

>>>>

The governing equation for $u(\xx,t)$ is obtained by computing the domain variation of the free energy $F$ \cite{Fu20}:
We obtain
a screened Laplace equation boundary value problem as a model for the hydrophobic interaction between water and JPs:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
With 
The boundary condition $g$ gives the degree of hydrophobicity the
particle-solvent interface.

@@

With max$(g)>0$ to guarantee (at least partial) hydrophobic surface on each JP,  
the boundary condition can be classified into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
these three categories correspond to three characteristic values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles and 60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayers for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.

Figure~\ref{fig:relax}(a) shows the initial configurations with orientations of 198-particle and 60- particle cases,
respectively. 
Case (i) with $b = 1$ (bc(i)) mimicks an amphiphilic particle.
The boundary condition $g$ is everywhere nonnegative,
takes the value $0$ on the
hydrophilic head (green),
and takes the maximum value $a$ on the
hydrophobic tail (red). 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for 60-particle run.
Both cases form bilayers with multiple components.

In case (ii) with $b = 1$ (bc(ii)) the boundary condition is everywhere positive.
It takes the maximum value $3a$ on tail (red) and the
minimum value $a$ on the head side (yellow). 
Both sides of the Janus particle are hydrophobic but
more so on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers form multilamella structures.
The number of folds depends primarily on the number of particles.
Figure~\ref{fig:relax}(c), for example, shows a
multilamellar structure with four layers and one with two layers in the inset.

In case (iii) with $b=1$ (bc(iii))
a water structure with
positive/negative charge is possible \cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
square grid and the orientations alternate
between layers (Figure~\ref{fig:relax}(d)).

@@

\subsection{Bilayer configurations (bc(i)) in a linear shear flow}
To begin, we place the bilayer structure (with bc(i)) from the inset of Figure~\ref{fig:relax}(b)
in a linear shear flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y\cdot\xx){\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate and ${\bf e}_x$ and ${\bf e}_y$
are horizontal and vertical unit vectors, respectively.  
The initial bilayer structure consists of a small self-enclosing bilayer (vesicle) and several pieces of bilayers.
Figure~\ref{fig:BC1_shear}(a)--(c)
shows snapshots of the bilayer when $\dot\gamma= 0.05,0.075,0.01$
at $t = 0.5$ $\upmu$s.
The dynamics of the bilayer can be found in the supplementary movies, which show that the initial pieces of bilayers merge and form a worm-like shape
under a linear shear flow.
At a low shear rate, the bilayer constantly goes through rotation and extensional deformation with the whole bilayer intact (figure~\ref{fig:BC1_shear}(a)).
As the shear rate increases to a moderate value (figure~\ref{fig:BC1_shear}(b)), the bilayer is observed to shed a small piece of bilayer, similar to the asymmetric breakup of a viscous drop \cite{}.
In figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two nearly equal bilayers, similar to the symmetric drop breakup under a linear shear flow \cite{}.
%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
 The streamlines are plotted in the background. 
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
  }
\end{figure}

In terms of deformations, 
the free energies 
are relatively constant (Figure~\ref{fig:BC1_shear}(d)),
with the overall changes in the range of a few kT/nm.  
Note that the free energy $F$ in figure~\ref{fig:BC1_shear}(d) has the unit of force because our system is two dimensional.

An interesting feature of the simulations is that the order parameter $\tilde S_2$ in (Figure~\ref{fig:BC1_shear}(e))
is on average increasing.  In the initial configuration,
the structure has three or four components.  
%
Under the shear flow, the shedding and merging of bilayers
result in an overall decrease in distinct bilayer structures.  
This suggests that
the shear flow changes the energy landscape to move the local equilibrium obtained from a random initial condition
to an alternate local equilibrium with greater orientational order.

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
  \end{center}
\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
}
\end{figure}
%
Finally, the strain parameter diverges in the large shear flow rate cases (Figure~\ref{fig:BC1_shear}(f))
because the components eventually completely separate and move away from one another
under the shear flow.

In \citet{Fu2022_JFM} the hydrodynamics of a JP vesicle under a linear shear flow is studied. 
Focusing on drawing analogies to hydrodynamics of a vesicle in continuum modeling (such as tank-treading, bilayer slip and permeability),
our previous studies also show the existence of a critical shear rate above which the JP vesicle ruptures. 
Based on the these early results, we conduct numerical simulations with $\dot\gamma=0.05, 0.066, 0.075$.
At these shear rates, the vesicle undergoes the familiar hydrodynamics (such as elongation along the extensional axis and tank-treading motion),
as shown in Figure~\ref{fig:Ves_shear} (a)--(c).
%
Here we illustrate how the three measures of structural deformation 
correlate to the dynamics of a JP vesicle.
We reinitialized the case (i) configuration with particles arranged in the pattern of a single, circular vesicle.
This shape is also a local equilibrium, with somewhat less energy than the disordered state c.f.,
Figure~\ref{fig:BC1_shear}(d) and Figure~\ref{fig:Ves_shear} (d).

Unlike the dynamics of bilayers in figure~\ref{fig:BC1_shear}, 
the energies of the JP vesicle in figure~\ref{fig:Ves_shear}(d) show jumps from the baseline value $30$ kT/nm to 32 kT/nm
signaling the rupture of the vesicle into multiple components
(Figure \ref{fig:Ves_shear}(d), long and short dashed curves).
After this initial break, the energies are more or less constant.
